\theseminartitle \\ \small \thetitle

### 2021-09-26 tex/paper.tex
Finished chapter about E-Divisive means

	\subsection{E-Divisive Means}
	\label{ssec:cp_edivisive}

@@

\section{Evaluation of Performance Results}
\label{sec:exp_evaluation}
\section{Reflection}

\section{Future Work}

>>>>

	\subsection{E-Divisive Means}
	\label{ssec:cp_edivisive}
	One algorithm for detecting change points is the E-Divisive Means algorithm. In contrast to other change point detection algorithms it offers a few benefits decribed by Daly et al. (See \cite{daly2020} p. 69):

	\begin{itemize}
		\item No distributional assumptions required
		\item Can identify multiple change points using recursion
		\item Does noit require training data
	\end{itemize}

	The algorithm is based on hierachically dividing the given time-series into multiple clusters. The recursive approach can be summarized in three steps:
	\begin{enumerate}
		\item For each point in the time series calculate a statistic $\hat{Q}$
		\item Select the largest $\hat{Q}$ as the next change point
		\item This divides the time series into two new clusters
	\end{enumerate}

	The termination of the algorithm for a specific cluster is determined by repeating the above steps on a random permutation of the input cluster data. If then the highest $\hat{Q}$ value does not significantly changes it is likely that the series does not contain a relevant change point.

	Within this paper the readily available python package implemented by engineers of MongoDB will be used\footnote{TODO: Link to GitHub}. A broad overview of the algorithm that includes the exact calculation of $\hat{Q}$ is described by the work of Daly et al. (\cite{daly2020} p. 69) while an in depth description of the algorithm is given in the original paper by Matteson and James (\cite{Matteson2014}).

@@

\section{Evaluation of Performance Results}
\label{sec:exp_evaluation}

\section{Reflection}

\section{Related Work}

\section{Conclusion}
